Cloud correction of humidity radiances with case-specific uncertainty estimate

### 2020-11-23 Article/ici_submm_cloudcorr.tex
added Simon's corrections

Although microwave channels are less affected by cloud contamination, precipitation and most dense clouds, particularly if found at high altitude, can
still affect measured radiances around 183\,GHz
\citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
then is dominated by scattering, the complexity of the analysis of the data
increases dramatically and there exists a need to identify the problematic
cases. This is normally denoted as cloud filtering, to obtain data of ``clear
sky'' character. Such filtering has been applied to derive climate records
\citep{lang2020new} and is essential in studies of the agreement between
observations and simulations \citep{brogniez2016review} as well as 
comparing observations of different instruments to validate their calibration
\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. Commonly
used cloud filtering methods for these applications are based on 183\,GHz data alone, involving rules on the brightness temperatures differences between channels \citep{burns1997effects, buehler:aclou:07}.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

@@

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest for testing.

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). The validation dataset is part of the training dataset which is held back during the training.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
	\caption{The distribution of point estimate (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 & $-$0.84 &$-$0.10 &$-$0.09 &$-$0.05 &$-$0.04 &$-$0.11 &$-$0.10 &$-$0.10 &$-$0.09 & 0.24  &$-$0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness &$-$0.02 &$-$12.72 &$-$1.17 &$-$1.00 &$-$1.06 &$-$0.90 &$-$1.16 &$-$1.04 &$-$1.78 &$-$1.71 &-1.95  &$-$3.45\\
Rejection& -	 &- 	  &-	  & 3.3\,\% &- 	  & 3.4\,\% &-     & 3.2\,\% &-     & 3.3\,\% & 28.8\,\%& 3.5\,\%\\
\bottomhline
	\end{tabular}
\end{table*}

Posterior distributions of $\ynfcs$ obtained from experiment 89+150\,GHz are similar to the ones shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K, occur too frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The appearance of a small positive tail also indicates overestimation in few cases. The corresponding error statistics (see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness ($-$12.72) and high bias ($-$0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to $-$0.10\,K. However, negative skewness indicates presence of  uncorrected departures. Including 118\,GHz in the training gives a small improvement compared to 89+150 GHz alone. The error distribution has lower bias and are more symmetric, but the MAE and standard deviation remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall performance is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.

@@

The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be the optimal. The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ As Table~\ref{tab:error_statistics_mwhs_14}, but for MWHS-2 channels 11, 12, 13, 15, and experiment QRNN-single 89+150\,GHz.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
		\cline{2-8}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
		&	&		   &			& All & Pred.(5\,K) &&\\
		\middlehline
		Channel 11  & Bias     &$-$0.00 & $-$0.15 &$-$0.12 &$-$0.12 &$-$0.04 &$-$0.05\\
					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
					& Skewness &  0.01 &$-$15.73 &$-$0.61 &$-$0.45 &$-$0.07 &$-$0.29\\
					& Rejection   & -    & -      & -	  & 0.2\,\% & 28.8\,\% & 3.5\,\%  \\
		\middlehline
		Channel 12  &  Bias     &$-$0.01 & $-$0.29 &$-$0.12 &$-$0.11  &$-$0.08 &$-$0.16\\
					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
					&  Skewness &$-$0.01 &$-$17.27 &$-$0.96 &$-$0.79  & $-$0.25 &$-$1.02 \\
					& Rejection & -     & -      & -	 & 0.6\,\%  & 28.8\,\% & 3.5\,\%  \\
		\middlehline
		Channel 13  &Bias       & 0.00 & $-$0.53 &$-$0.11 &$-$0.10 &$-$0.14 &$-$0.31\\
					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
					&Skewness   & 0.01 &$-$15.24 &$-$1.22 &$-$1.08 &$-$1.03 &$-$2.30\\  	
					& Rejection & -     & -      & -	 & 1.6\,\%& 28.8\,\% & 3.5\,\%  \\	
		\middlehline
		Channel 15  &  Bias     & 0.00 & $-$1.28 &$-$0.09 &$-$0.07 &$-$0.33 &$-$0.83\\
					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
					&  Skewness & 0.00 &$-$10.11 &$-$0.69 &$-$0.82 &$-$2.87 & $-$4.33 \\ 
					& Rejection & -     & -      & -	 & 5.5\,\% & 28.8\,\%& 3.5\,\%  \\
		\bottomhline
	\end{tabular}
\end{table*}

@@

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig05.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K. For each quantile, the sample variation is also shown as box plot. }
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI). For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/fig07.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN is trained five times for each 183\,GHz channel as target. Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels. 	
\end{enumerate}

@@

		\middlehline
		AWS-34	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
				&Skewness &$-$0.01 &$-$11.06 &$-$3.53 &$-$1.02  \\
		\middlehline
		AWS-35	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
				&Skewness &  0.00 &$-$13.43 &$-$2.46 &$-$0.62  \\
		\middlehline
		AWS-36  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
				&Skewness &  0.00 &$-$13.54 &$-$1.32 &$-$0.27  \\
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
In an analogy between the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}. For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively. However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively. A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact. Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution. This is most likely due to rejection of cases affected by over-estimation. For AWS-33, the predictions have slightly higher accuracy than AWS-32. The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations. High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations. Nonetheless, filtering such cases makes the distribution more symmetric. For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter. For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.  Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.

@@

Figure~\ref{fig:calibration_I2V} shows the calibration of the prediction intervals for I2V. The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve. Similar is the case, when cases with correction greater than 5\,K are considered. On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is only slightly worse. In spite of the fact that such cases are few (~2\,\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases. For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).

>>>>

Although microwave channels are less affected by cloud contamination, precipitation and most dense clouds, particularly if found at high altitude, can
still affect measured radiances around 183\,GHz
\citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
then is dominated by scattering, the complexity of the analysis of the data
increases dramatically and there exists a need to identify the problematic
cases. This is normally denoted as cloud filtering, to obtain data of ``clear
sky'' character. Such filtering has been applied to derive climate records
\citep{lang2020new} and is essential in studies of the agreement between
observations and simulations \citep{brogniez2016review} as well as 
comparing observations of different instruments to validate their calibration
\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. Commonly
used cloud filtering methods for these applications are based on 183\,GHz data alone, involving rules on the brightness temperature differences between channels \citep{burns1997effects, buehler:aclou:07}.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

@@

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the remaining 23\,000 for testing.

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). The validation dataset is a separate part of the training dataset which is held back during the training.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
	\caption{The distribution of point estimates (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred. (5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred. (5\,K) & All & Pred. (5\,K) & All & Pred. (5\,K)  & All & Pred. (5\,K)&&\\
		\middlehline
Bias     &  0.00 & $-$0.84 &$-$0.10 &$-$0.09 &$-$0.05 &$-$0.04 &$-$0.11 &$-$0.10 &$-$0.10 &$-$0.09 & 0.24  &$-$0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness &$-$0.02 &$-$12.72 &$-$1.17 &$-$1.00 &$-$1.06 &$-$0.90 &$-$1.16 &$-$1.04 &$-$1.78 &$-$1.71 &-1.95  &$-$3.45\\
Rejection& -	 &- 	  &-	  & 3.3\,\% &- 	  & 3.4\,\% &-     & 3.2\,\% &-     & 3.3\,\% & 28.8\,\%& 3.5\,\%\\
\bottomhline
	\end{tabular}
\end{table*}

Posterior distributions of $\ynfcs$ obtained from experiment 89+150\,GHz are similar to the ones shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K, occur too frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The appearance of a small positive tail also indicates overestimation in few cases. The corresponding error statistics (see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness ($-$12.72) and high bias ($-$0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to $-$0.10\,K. However, negative skewness indicates presence of  uncorrected departures. Including 118\,GHz in the training gives a small improvement compared to 89+150 GHz alone. The error distribution has lower bias and is more symmetric, but the MAE and standard deviation remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall performance is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.

@@

The three experiments were also performed for the other four 183\,GHz channels, and a similar performance was obtained (not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be optimal. The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.

@@

\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
\label{sec:mwhs_others}
\begin{table*}[t]
	\caption{ As Table~\ref{tab:error_statistics_mwhs_14}, but for MWHS-2 channels 11, 12, 13, 15, and experiment QRNN-single 89+150\,GHz.}
	\label{tab:error_statistics_mwhs_others}
	\begin{tabular}{lrrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
		\cline{2-8}
		%		\hline
		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
		&	&		   &			& All & Pred. (5\,K) &&\\
		\middlehline
		Channel 11  & Bias     &$-$0.00 & $-$0.15 &$-$0.12 &$-$0.12 &$-$0.04 &$-$0.05\\
					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
					& Skewness &  0.01 &$-$15.73 &$-$0.61 &$-$0.45 &$-$0.07 &$-$0.29\\
					& Rejection   & -    & -      & -	  & 0.2\,\% & 28.8\,\% & 3.5\,\%  \\
		\middlehline
		Channel 12  &  Bias     &$-$0.01 & $-$0.29 &$-$0.12 &$-$0.11  &$-$0.08 &$-$0.16\\
					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
					&  Skewness &$-$0.01 &$-$17.27 &$-$0.96 &$-$0.79  & $-$0.25 &$-$1.02 \\
					& Rejection & -     & -      & -	 & 0.6\,\%  & 28.8\,\% & 3.5\,\%  \\
		\middlehline
		Channel 13  &Bias       & 0.00 & $-$0.53 &$-$0.11 &$-$0.10 &$-$0.14 &$-$0.31\\
					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
					&Skewness   & 0.01 &$-$15.24 &$-$1.22 &$-$1.08 &$-$1.03 &$-$2.30\\  	
					& Rejection & -     & -      & -	 & 1.6\,\%& 28.8\,\% & 3.5\,\%  \\	
		\middlehline
		Channel 15  &  Bias     & 0.00 & $-$1.28 &$-$0.09 &$-$0.07 &$-$0.33 &$-$0.83\\
					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
					&  Skewness & 0.00 &$-$10.11 &$-$0.69 &$-$0.82 &$-$2.87 & $-$4.33 \\ 
					& Rejection & -     & -      & -	 & 5.5\,\% & 28.8\,\%& 3.5\,\%  \\
		\bottomhline
	\end{tabular}
\end{table*}

@@

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig05.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K. For each quantile, the sample variation is also shown as box plot. }
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI). For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/fig07.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from a posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

@@

	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz. This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available. In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel. For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44. QRNN is trained five times for each 183\,GHz channel as target. Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels. 	
\end{enumerate}

@@

		\middlehline
		AWS-34	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
				&Skewness &$-$0.01 &$-$11.06 &$-$3.53 &$-$1.02  \\
		\middlehline
		AWS-35	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
				&Skewness &  0.00 &$-$13.43 &$-$2.46 &$-$0.62  \\
		\middlehline
		AWS-36  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
				&Skewness &  0.00 &$-$13.54 &$-$1.32 &$-$0.27  \\
		\bottomhline				
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}. For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively. However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively. A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact. Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution. This is most likely due to rejection of cases affected by over-estimation. For AWS-33, the predictions have slightly higher accuracy than AWS-32. The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations. High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations. Nonetheless, filtering such cases makes the distribution more symmetric. For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter. For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.  Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.

@@

Figure~\ref{fig:calibration_I2V} shows the calibration of the prediction intervals for I2V. The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve. Similar is the case, when cases with correction greater than 5\,K are considered (not shown). On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is  slightly worse. In spite of the fact that such cases are few (2\,\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases. For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).
